Robust Spectroscopic Inference with Imperfect Models

### 2014-09-10 tex/paper.tex
more orders

We choose to do linear interpolation, but empirically determine the interpolation error by a series of ``drop-out'' interpolation tests, whereby we remove a spectrum from the grid, for example T=6000, logg=4.5, and Z=-0.5, and then create three sets of interpolated spectra, over the various dimensions. Therefore, for each spectrum in the synthetic grid, there are also three error spectra Generally, the interpolation error is small, typically no larger than 1\% across many lines. This test gives us confidence that it is possible to generate an interpolated spectra, and that inference on the stellar parameters may be drawn at a substantially finer level that the coarsity of the grid spacing itself. However, while the interpolation error is small, it is often the case that the error adds \emph{coherently}. When the signal to noise of the spectrum is particularly large, this coherent trend can manifest itself as a behavior that the spectral lines in an interpolated spectrum are less ``physical'' looking than those directly near a gridpoint, with minor or no interpolation. Therefore, it is necessary to quantify the degree of interpolation error, in order to give the proper likelihood to interpolated spectra.

[Figure here of actuall interpolation error, as alluded to in text].

[Possible second figure showing a 3D cube, with vertices labelled].

>>>>

We choose to do linear interpolation, but empirically determine the interpolation error by a series of ``drop-out'' interpolation tests, whereby we remove a spectrum from the grid, for example T=6000, logg=4.5, and Z=-0.5, and then create three sets of interpolated spectra, over the various dimensions. Therefore, for each spectrum in the synthetic grid, there are also three error spectra Generally, the interpolation error is small, typically no larger than 1\% across many lines. This test gives us confidence that it is possible to generate an interpolated spectra, and that inference on the stellar parameters may be drawn at a substantially finer level that the coarsity of the grid spacing itself, especially given the multitude of possible lines to fit. However, while the interpolation error is small, it is often the case that the error adds \emph{coherently}. When the signal to noise of the spectrum is particularly large, this coherent trend can manifest itself as a behavior that the spectral lines in an interpolated spectrum are less ``physical'' looking than those directly near a gridpoint, with minor or no interpolation. Therefore, it is necessary to quantify the degree of interpolation error, in order to give the proper likelihood to interpolated spectra.

\begin{figure}[!t]
\begin{center}
  \includegraphics{figs/interp_errors.pdf}
  \figcaption{Also showing the envelope for a two gridpoint interpolation. All errors measured relative to the value of the true spectrum.}
  \label{fig:interp_errors}
\end{center}
\end{figure}

Nearly all interpolation errors are below the spread in change for an interpolated value. Those few pixels for which the change in value is \emph{less} than the bracketed change are due to values for which the pixel value changes non-monotonically with parameters. In such a situation, because the synthetic grid is not Nyquist sampled, it is difficult to accurately predict what the true pixel value should be. In this case, the most conservative approach is to incorporate the large interpolation error budget, as we do.

\begin{figure}[!t]
\begin{center}
  \includegraphics{figs/interp_grid.pdf}
  \figcaption{Tri-linear interpolation on a grid cell the shape of a rectangular prism.}
  \label{fig:interp_grid}
\end{center}
\end{figure}
